---
title: "08 - More CSS!"
subtitle: "Professional, Polished, Presentable"
author: "Dr. Avahi Cleesei"
institute: "Bemaraha University, Madagascar"
date: "2021-07-07"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=2,
  out.width = "100%"
)
```

```{r xaringanthemer, echo=FALSE}
library(xaringanthemer)

palette <- c(
  orange      = "#fb5607",
  pink        = "#ff006e",
  blue_violet = "#8338ec",
  zomp        = "#38A88E",
  shadow      = "#87826E"
)

style_duo_accent(colors = palette)
```

class: center middle

🗺  [More CSS](https://presentable-user2021.netlify.app/materials/act-03/08-more-css)

---
class: scientific-names

# Woolly Lemurs

.common-name[Woolly lemurs] have short woolly fur and take long naps to digest their food.

There are **9** .species[species] in the .genus[Avahi] genus, here are **4** of them:

.lemur.eastern[
.common-name[Eastern] woolly lemur, .sci-name[.genus[Avahi] .species[laniger]]
]

.lemur.western[
.common-name[Western] woolly lemur, .sci-name[.genus[Avahi] .species[occidentalis]]
]

.lemur.sambirano[
.common-name[Sambirano] woolly lemur, .sci-name[.genus[Avahi] .species[unicolor]]
]

.lemur.bemaraha[
.common-name[Bemaraha] woolly lemur, .sci-name[.genus[Avahi] .species[cleesei]]
]

<style>
.lemur {
  color: var(--shadow);
}
.lemur .common-name {
  color: var(--orange);
}
.sci-name {
  font-style: italic;
}
.sci-name .genus {
  color: var(--zomp);
  font-weight: bold;
}
.sci-name .species {
  color: var(--blue_violet)
}
.lemur.bemaraha {
  font-weight: bold;
}
</style>
